---
title: "Vehicle MPG Prediction Based on mtcars"
author: "Peng"
date: "January 21, 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This presentation and the application was build as the project homework for the course Developing Data Products.

The Shiny application developed is available at:  https://pzeng123.shinyapps.io/shiny-application-and-reproducible-pitch/

The source codes of ui.R and server.R are available on the GitHub repo: https://github.com/pzeng123/Shiny-Application-and-Reproducible-Pitch

## Data

 `mtcars` dataset from datasets library is used.
 
```{r echo = TRUE}
summary(mtcars)
```

## Model

`lm` is used to fit a multivariable regression; `mpg` as outcome; `am`, `cyl`, `hp`, and `wt` as predictors:


```{r cars, echo = TRUE}
lm(formula = mpg ~ am + cyl + hp + wt, data = mtcars)
```

## Results

Users are able to predict their vehicles' MPG by selecting the transmission type, weight, horse power, and number of cylinders.

